---
title: "Validation of Resource model adds on to Prem et al COVID19 model"
author: "Arata Hidano"
date: "02/04/2020"
output: html_document
---

Setup reading source files, make sure you run this with appropriate path to the folder with data/codes
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = getwd())
require(ggplot2)
require(patchwork)
# load relevant the data files
source('1_loadData.r')

# source the age-structured SEIcIscR model functions 
source('function_modelSEIcIscRBCZ_validation.r')


# simulate N oubtreaks
source('2_simOutbreak_ncov_SEIcIscRBCZ.r')

```

##### Validation 1: Deterministic resource model

##### 1. Baseline deterministic model results for Wuhan population
##### 2. Impact of different R0 on the largest number of ICU required on a given day

```{r, echo=FALSE,message=F}
# Show only deterministic model results
X=epi_doNothingDurInf3[[1]]$time

ICU_det <- ggplot()+
  ggtitle("(1) Number of required ICU over time")+
  labs(x="Time(days)", y="Number of ICU")+theme_bw()

ICU_peak_R0 <- ggplot()+
  ggtitle("(2) The peak number of ICU required across sampled R0 value")+
  labs(x="R0", y="Number of peak ICU")+theme_bw()
for(i in 1:nsim)
{
  sum_ICU_det <- rowSums(epi_doNothingDurInf3[[i]]$ICU_det)
  R0 <- epi_doNothingDurInf3[[i]]$R0t
  peak <- max(rowSums(epi_doNothingDurInf3[[i]]$ICU_det))
  #sum_ICU_stochastic <- rowSums(epi_doNothingDurInf3[[i]]$ICU)
  ICU_det <- ICU_det + geom_line(aes_string(x=X, y=sum_ICU_det),color="steelblue",size=1,alpha=0.5)
    # geom_line(aes_string(x=X, y=sum_ICU_stochastic),color="red",size=1,alpha=0.5)
  ICU_peak_R0 <- ICU_peak_R0 + geom_point(aes_string(x=R0, y=peak),color="black",size=1)
}
v1<-ICU_det+ICU_peak_R0
v1
ggsave("Validation_1.png",v1)


```

##### Validation 2: Stochastic resource model compared to deterministic model

##### 3. Number of required ICU over time
##### 4. Number of required Bed over time

```{r, echo=FALSE,warning=F,message=F}
# Compare Deterministic and stochastic model
# ICU
sum_ICU_det <- rowSums(epi_doNothingDurInf3[[1]]$ICU_det)
X=epi_doNothingDurInf3[[1]]$time

ICU_comparison <- ggplot()+geom_line(aes_string(x=X, y=sum_ICU_det),color="black",size=1.5)+
  ggtitle("(3) Number of required ICU over time")+
  labs(x="Time(days)", y="Number of ICU")+theme_bw()


for(i in 1:nsim)
{
  sum_ICU_stochastic <- rowSums(epi_doNothingDurInf3[[i]]$ICU)
  ICU_comparison <- ICU_comparison + geom_line(aes_string(x=X, y=sum_ICU_stochastic),color="steelblue",size=0.5,alpha=0.5)
  
}


#BED
sum_BED_det <- rowSums(epi_doNothingDurInf3[[1]]$BED_det)
X=epi_doNothingDurInf3[[1]]$time

BED_comparison <- ggplot()+geom_line(aes_string(x=X, y=sum_BED_det),color="black",size=1.5)+
  ggtitle("(4) Number of required BED over time")+
  labs(x="Time(days)", y="Number of BED")+theme_bw()


for(i in 1:nsim)
{
  sum_BED_stochastic <- rowSums(epi_doNothingDurInf3[[i]]$BED)
  BED_comparison <- BED_comparison + geom_line(aes_string(x=X, y=sum_BED_stochastic),color="steelblue",size=0.5,alpha=0.5)
  
}
v2<-ICU_comparison+BED_comparison
v2
ggsave("Validation_2.png",v2)
# Note that they're showing only one deterministic model result (shown in black line) with a specific R0
```

##### Validation 3: Stochastic model results compared to pre-defined parameters

##### 5. Impact of different stochastic formulation. 

Output of the deterministic mode needs to be forced into integers, either by taking floor (red), round (black), or
ceiling (blue). This shows the impact is minimal, however, we chose round function to minimise the artefact overestimation. 
```{r}
# Check cumulative number of FA, BED, ICU against that of Ic
# Retrieve parameters
durDelay = 7;                                                 # Median time from symptom onset to hospital admission Wang et al 2020
delta = 0.2;                                                       # proportion of clinical cases that develop severe signs
theta = 1-exp(-1/durDelay);                                       # Probability of hospital admission after symptom onset
epsilon = 0.26 
```

```{r,echo=F,warning=F,message=F}
# Proportion of severe cases among clinical cases observed in the model over time against the 'true' value
X=epi_doNothingDurInf3[[1]]$time

cum_Ic_FA_all <- ggplot()+geom_hline(aes(yintercept = delta),color="black",size=0.5)+
  ggtitle("(5) Propotion of severe cases \n among clinical cases over time")+
  labs(x="Time(days)", y="Proportion")+theme_bw()

for(i in 1:nsim)
{
  sum_Ic_stochastic <- rowSums(epi_doNothingDurInf3[[i]]$cum_Ic)
  sum_FA_stochastic <- rowSums(epi_doNothingDurInf3[[i]]$cum_FA)
  sum_FA_stochastic_f <- rowSums(epi_doNothingDurInf3[[i]]$cum_FA_f)
  sum_FA_stochastic_r <- rowSums(epi_doNothingDurInf3[[i]]$cum_FA_r)
  prop <- sum_FA_stochastic/sum_Ic_stochastic
  prop_f <-  sum_FA_stochastic_f/sum_Ic_stochastic
  prop_r <-  sum_FA_stochastic_r/sum_Ic_stochastic
  cum_Ic_FA_all <- cum_Ic_FA_all+ 
    geom_line(aes_string(x=X, y=prop_f),color="red",size=0.5,alpha=0.5)+
    geom_line(aes_string(x=X, y=prop),color="steelblue",size=0.5,alpha=0.5)+
    geom_line(aes_string(x=X, y=prop_r),color="black",size=0.5,alpha=0.5)
}

# Proportion of ICU cases among severe cases observed in the model over time against the true value
X=epi_doNothingDurInf3[[1]]$time

cum_ICU_FA <- ggplot()+geom_hline(aes(yintercept = epsilon),color="black",size=0.5)+
  ggtitle("(6) Propotion of ICU cases \n among severe cases over time")+
  labs(x="Time(days)", y="Proportion")+theme_bw()


for(i in 1:nsim)
{
  sum_ICU_stochastic <- rowSums(epi_doNothingDurInf3[[i]]$cum_ICU_r)
  sum_FA_stochastic <- rowSums(epi_doNothingDurInf3[[i]]$cum_FA_r)
  prop <- sum_ICU_stochastic/sum_FA_stochastic
  cum_ICU_FA <- cum_ICU_FA + geom_line(aes_string(x=X, y=prop),color="steelblue",size=0.5)
  
}

v3 <- cum_Ic_FA_all + cum_ICU_FA
v3
ggsave("Validation_3.png",v3)

```
